------
##title: "R4DS Assignment2"   
output: html_notebook   
        keep_md: true   
------
##Group members:  
  Sihan Liu  
  Diksha Motwani  
  Jing Ouyang  
  Haohao Xu  
  Ruilin Ye  


###3.2.5 What happens if you make a scatterplot of `class` vs `drv`? Why is the plot not useful?

```{r}
library("tidyverse")
```

```{r}
ggplot(mpg, aes(x = class, y = drv)) + geom_point()
```
A scatter plot is not a useful display of these variables since both drv and class are categorical variables.

###3.3.2 Which variables in `mpg` are categorical? Which variables are continuous? (Hint: type `?mpg` to read the documentation for the dataset). How can you see this information when you run `mpg`?


The following list contains the categorical variables in mpg.

    model
    trans
    drv
    fl
    class

The following list contains the continuous variables in mpg.

    displ
    year
    cyl
    cty
    hwy
    
```{r}
mpg
```

Those with <chr> above their columns are categorical, while those with <dbl> or <int> are continuous. 

###3.6.1 What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?


    line chart: `geom_line()`
    boxplot: `geom_boxplot()`
    histogram: `geom_hist()`
    area chart: `geom_area()`

###4.3 Press Alt + Shift + K. What happens? How can you get to the same place using the menus?

This gives a menu with keyboard shortcuts. This can be found in the menu under `Tools -> Keyboard Shortcuts Help`.



